When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2017-11-10 paper/paper.tex
Notation
emphasis -> emphasise

For larger patterns, more complex behaviour emerges. If we are in the intersection of the bottom half
and the bottom right diagonal of the search space, we should always retain the original heuristic,
and if we are in the intersection of the top half and the top left diagonal, we should always use
the complements. This behaviour can be predicted by taking the partial derivatives of $\langle Sol
\rangle$ in the $-p_d$ and $t_d$ directions.  However, when inside the remaining two eighths of the
parameter space, the partial derivatives of $\langle Sol \rangle$ disagree on which heuristic to
use, and using directional derivatives is not enough to resolve the problem. A close observation of
the data suggests that the actual location of the phase transition may be involved (and perhaps
\citeauthor{DBLP:conf/aaai/Walsh98}'s suggestion applies only in these conditions). In any case, $\langle Sol
\rangle$ is insufficient to explain the observed behaviour in these two eighths of the parameter space.

@@

We saw in the previous sections that although permuting input graphs could improve VF2's behaviour
on some instances, doing so does not make its performance come close to that of domain-based
algorithms.  \citeauthor{DBLP:conf/edbt/KatsarouNT17} say they ``hope that our findings will open up
new research directions, striving to find appropriate, per-query, isomorphic rewritings, in
combination with alternate per-query sub-iso algorithms that can yield large improvements''. We
believe it is important instead to emphasis previous research directions that have already solved
most of this problem, and to help ensure that these techniques become more widely known.

>>>>

For larger patterns, more complex behaviour emerges. If we are in the intersection of the bottom half
and the bottom right diagonal of the search space, we should always retain the original heuristic,
and if we are in the intersection of the top half and the top left diagonal, we should always use
the complements. This behaviour can be predicted by taking the partial derivatives of $\langle Sol
\rangle$ in the $-p_d$ and $d_t$ directions.  However, when inside the remaining two eighths of the
parameter space, the partial derivatives of $\langle Sol \rangle$ disagree on which heuristic to
use, and using directional derivatives is not enough to resolve the problem. A close observation of
the data suggests that the actual location of the phase transition may be involved (and perhaps
\citeauthor{DBLP:conf/aaai/Walsh98}'s suggestion applies only in these conditions). In any case, $\langle Sol
\rangle$ is insufficient to explain the observed behaviour in these two eighths of the parameter space.

@@

We saw in the previous sections that although permuting input graphs could improve VF2's behaviour
on some instances, doing so does not make its performance come close to that of domain-based
algorithms.  \citeauthor{DBLP:conf/edbt/KatsarouNT17} say they ``hope that our findings will open up
new research directions, striving to find appropriate, per-query, isomorphic rewritings, in
combination with alternate per-query sub-iso algorithms that can yield large improvements''. We
believe it is important instead to emphasise previous research directions that have already solved
most of this problem, and to help ensure that these techniques become more widely known.
